Diffantom: a whole-brain diffusion MRI phantom derived from a real dataset

### 2015-08-12 paper/main.tex
trying to clarify the model. close #17

The process to obtain the microstructural model can be described like follows:
1) The fiber orientation maps $\{\mathbf{V}_i\}$ and their corresponding fiber-fraction maps $\{F_i\}$ are
  obtained using the ball-and-stick model for multi-shell data of BEDPOSTX \citep{jbabdi_modelbased_2012}
  on the \gls*{dmri} data of a certain \gls*{hcp} subject.
2) A \gls*{fa} map is obtained after fitting a tensor model with \emph{MRTrix}.
3) The original fiber-fractions and the \gls*{fa} map are denoised with a non-local means filter included
  in \emph{dipy} \citep{garyfallis_dipy_2011}.
This step produces an important smoothing of the maps, while preserving edges in them.
It is also beneficial in simplifying the voxel-wise diffusion model.
4) The macrostructural 5TT map $\{T'_j\}$ is extracted from the \acrlong*{t1} image of the subject, using \emph{MRTrix} tools.
5) The objects obtained in the previous steps are combined as described in the \nameref{sec:appendix} to generate the
  microstructural model, presented in \autoref{fig:figure1}-A.

>>>>

The process to obtain the microstructural model from one dataset of the \gls*{hcp} can be described
  like follows:
1) The fiber orientation maps $\{\mathbf{V}_i\}$ and their corresponding estimations of volume fraction $\{F'_i\}$ are
  obtained using the ball-and-stick model for multi-shell data of \emph{bedpostx} \citep{jbabdi_modelbased_2012}
  on the \gls*{dmri} data.
The \gls*{hcp} indicates \emph{bedpostx} to reconstruct their data \citep{glasser_minimal_2013}.
Additionally, this software was able to exploit the multi-shell acquisitions of the \gls*{hcp} while
  operating at whole-brain level.
2) A \gls*{fa} map is obtained after fitting a tensor model with \emph{MRTrix}.
The \gls*{fa} is used to infer $F_1$ (the fraction map of the most prevalent fiber), avoiding the extremely
  noisy estimation of $F'_1$ performed by \emph{bedpostx} in the previous step.
3) The original fiber fractions $\{F'_i\}$ and the \gls*{fa} map are denoised with a nonlocal means filter included
  in \emph{dipy} \citep{garyfallis_dipy_2011}.
This step produces an important smoothing of the maps, while preserving the edges in them.
Smoothing is also beneficial in simplifying the voxel-wise diffusion model.
4) The macrostructural fractions $\{T'_j\}$ are extracted from the \acrlong*{t1} image of the dataset,
  using standard \emph{FSL} segmentation tools \citep{jenkinson_fsl_2012}.
5) The images obtained previously (\gls*{fa} map, $\{\mathbf{V}_i\}$, $\{F'_i\}$, and $\{T'_j\}$)
  are combined as described in the \nameref{sec:appendix} to generate the final microstructural model
  ($\{\mathbf{V}_i\}$, $\{F_i\}$, and $\{T_j\}$), presented in \autoref{fig:figure1}-A.
